The Hyperedge Event Model

### 2018-10-06 paper/revision1/ba-sample.tex
adding lit discussion

	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern hyperedge event formation: (1) the formation of the vertices that are incident to the hyperedge, and (2) the timing of the hyperedge event. In what follows, we define the HEM's generative process for hyperedge event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference, and present tests of our software implementation (Section \ref{sec:inference}). We then demonstrate our model's applicability in a case study (Section \ref{sec:Emails}) where we analyze a corpus of internal county government emails and illustrate how to perform model selection, posterior predictive checks, and exploratory analysis using our model. We conclude in Section \ref{sec:conclusion}.~\looseness=-1

>>>>

	We develop a statistical dynamic network model, which we term the hyperedge event model (HEM), that integrates the two components that govern hyperedge event formation: (1) the formation of the vertices that are incident to the hyperedge, and (2) the timing of the hyperedge event. Though the HEM, based on our knowledge of the literature, is unique in modeling hyperedge events in continuous time, we build our model using features inspired by many of the existing models for dynamic network data. First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie). The HEM's use of subgraph configuration formation follows very similar aspects of the continuous-time event model proposed by \cite{PerryWolfe2012}, [HERE]

In what follows, we define the HEM's generative process for hyperedge event data (Section \ref{sec:generative process}), derive the conditional posteriors for Bayesian inference, and present tests of our software implementation (Section \ref{sec:inference}). We then demonstrate our model's applicability in a case study (Section \ref{sec:Emails}) where we analyze a corpus of internal county government emails and illustrate how to perform model selection, posterior predictive checks, and exploratory analysis using our model. We conclude in Section \ref{sec:conclusion}.~\looseness=-1
